---
title: "Dashboard Hub"
output: 
  distill::distill_article:
    css: "css/strapless.css"
    toc: true
    toc_depth: 3
    toc_float: true
---

The following dashboards are organized according to our <a href = "https://datahub.teachinglab.org/evaluation_plan.html">evaluation plan</a> and can also be found at the <a href = "https://docs.google.com/document/d/1yvo1cW5i3OXtzN3Lf1lCRgw06Efbt0CH7n6PM53kELI/edit">data collection overview and data access guide</a>.

## Participant Perceptions

Participant perceptions include data from the end of session survey administered at the end of each PL session, end of course survey administered at the end of each PL course, ongoing coaching survey administered at the end of each coaching session, and end of coaching data, administered at the end of every coaching series. Lastly, NPS data is also prompted in this survey.
<br>

```{r participant-feedback-surveys, echo = F, layout = "l-body-outset"}
library(htmltools)
library(bslib)
layout_column_wrap(
  width = 1 / 3,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Participant Feedback Full Report", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section2", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section2"
    ),
    card_footer("View all forms of p+articipant feedback and NPS simultaneously in section 2")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Participant Feedback Internal Rollup", href = "https://teachinglabhq.shinyapps.io/tl_facilitator_data/", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/FacilitatorRollup.png",
      href = "https://teachinglabhq.shinyapps.io/tl_facilitator_data/"
    ),
    card_footer("View all participant feedback data with additional functionality and time-incorporated data")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Participant Feedback Qualtrics Data", href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/web/6317cbd1f9feca001046524d", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/web/6317cbd1f9feca001046524d"
    ),
    card_footer(
      tags$a("Access qualtrics dashboards using the information here", href = "https://docs.google.com/document/d/1oD5mCtSMK8atMZknPruhgf6qToAA5oF7HyZQTil3i4w/edit")
    )
  )
)
```

## Participant Mindsets

Participant mindsets come from the diagnostic educator survey and follow up educator survey.

```{r educator-surveys, echo = F, layout = "l-body-outset"}
layout_column_wrap(
  width = 1 / 2,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Educator Survey Full Report", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section4", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section4"
    ),
    card_footer("View demographic information in section 1, teacher mindsets in section 4, and school leader mindsets in section 5")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Educator Survey Qualtrics Data", href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/63053d35379f890010cc456e?pageId=Page_fcc6840b-679e-4652-b50c-6a95853b5887", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/63053d35379f890010cc456e?pageId=Page_fcc6840b-679e-4652-b50c-6a95853b5887"
    ),
    card_footer(
      tags$a("Access qualtrics dashboards using the information here", href = "https://docs.google.com/document/d/1oD5mCtSMK8atMZknPruhgf6qToAA5oF7HyZQTil3i4w/edit")
    )
  )
)
```

## Participant Knowledge

Participants that completed <a href = "https://docs.google.com/document/d/1t43JudOR4AlIk8ALdPp1V9UgZH8mWmybrDdDp2085mQ/edit?usp=sharing">course assessments</a> will answer multiple choice quiz questions that address pedagogical content knowledge.

```{r course-assessments, echo = F, layout = "l-body-outset"}
layout_column_wrap(
  width = 1 / 2,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Course Assessments Dashboard", href = "https://teachinglabhq.shinyapps.io/course_assessments/", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/CourseAssessment.png",
      href = "https://teachinglabhq.shinyapps.io/course_assessments/"
    ),
    card_footer("View course assessments data as % correct before/after, % correct by each question, and finally % selected within each question!")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Course Assessments Ongoing Report", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section3", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section3"
    ),
    card_footer("Additionally view overall course assessments data in the ongoing report.")
  )
)
```

## Participant Practices

Teaching Lab staff conduct classroom observations and capture <a href = "https://achievethecore.org/category/1155/printable-versions">standards and shifts aligned instruction</a> in the classroom observations survey. Those results will appear in the following dashboards.

```{r ipg-data, echo = F, layout = "l-body-outset"}
layout_column_wrap(
  width = 1 / 4,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("IPG Raw Data/Downloadable Dashboard", href = "https://teachinglabhq.shinyapps.io/IPGRawDataDashboard/", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/IPGRawDashboard.png",
      href = "https://teachinglabhq.shinyapps.io/IPGRawDataDashboard/"
    ),
    card_footer("Download classroom observations data in a rolled up summative form, or view entire responses on a per-teacher basis")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("IPG Ongoing Report Data", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section6", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section6"
    ),
    card_footer("View % positive indicators in section 6b and 6c.")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("IPG Qualtrics Data", href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/web/6349bfbbb614690016a0b7b1/pages/Page_120ba1a8-cea1-44d2-a7e0-19fd41fcc67a/view", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/web/6349bfbbb614690016a0b7b1/pages/Page_120ba1a8-cea1-44d2-a7e0-19fd41fcc67a/view"
    ),
    card_footer(
      tags$a("Access qualtrics dashboards using the information here", href = "https://docs.google.com/document/d/1oD5mCtSMK8atMZknPruhgf6qToAA5oF7HyZQTil3i4w/edit")
    )
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Google Sheets Classroom Observations Qualtrics Copy", href = "https://docs.google.com/spreadsheets/d/1mRZThJuslwVGXyWNY2Z-gAgh0FZKaJM1LIHRwhRvMg8/edit#gid=1191104641", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://docs.google.com/spreadsheets/d/1mRZThJuslwVGXyWNY2Z-gAgh0FZKaJM1LIHRwhRvMg8/edit#gid=1191104641"
    ),
    card_footer("A google sheet with all qualtrics data, each tab contains responses from a specific IPG rubric.")
  )
)
```

## Student Learning Experiences

Respondents to the student survey and submissions of student work samples have their responses rolled up and graded in the following dashboards.

```{r student-survey, echo = F, layout = "l-body-outset"}
layout_column_wrap(
  width = 1 / 3,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Student Outcomes Ongoing Report", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section7", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section7"
    ),
    card_footer("View % agree/strongly agree on the student survey and eic student survey in section 7a (data not shown if site is not applicable).")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Student Survey Qualtrics Data", href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/6345c33160c27c00166cb726?pageId=Page_ee9d1195-c476-4414-b1ab-ee2da2fdb4ce", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/6345c33160c27c00166cb726?pageId=Page_ee9d1195-c476-4414-b1ab-ee2da2fdb4ce"
    ),
    card_footer(
      tags$a("Access qualtrics dashboards using the information here", href = "https://docs.google.com/document/d/1oD5mCtSMK8atMZknPruhgf6qToAA5oF7HyZQTil3i4w/edit")
    )
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("EIC Student Survey Qualtrics Data", href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/636172f94060140010530cc8?pageId=Page_35ff03a3-5111-48b5-abcd-ecfca4249e62", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/QualtricsLogo.png",
      href = "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/636172f94060140010530cc8?pageId=Page_35ff03a3-5111-48b5-abcd-ecfca4249e62"
    ),
    card_footer(
      tags$a("Access qualtrics dashboards using the information here", href = "https://docs.google.com/document/d/1oD5mCtSMK8atMZknPruhgf6qToAA5oF7HyZQTil3i4w/edit")
    )
  )
)
```

```{r student-work, echo = F, layout = "l-body-outset"}
layout_column_wrap(
  width = 1 / 3,
  height = 400,
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Student Work Graded Summaries", href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section7", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Reports/23_24/Ongoing23_24Report.png",
      href = "https://teachinglabhq.shinyapps.io/OngoingReport_23_24/?section=section7"
    ),
    card_footer("View graded student work assignments breakdowns in sections 7b and 7c.")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Student Work Grading Web App", href = "https://teachinglabhq.shinyapps.io/student_work_samples/", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/StudentWorkGrader.png",
      href = "https://teachinglabhq.shinyapps.io/student_work_samples/"
    ),
    card_footer("Grade student work assignments that have been submitted to Teaching Lab!")
  ),
  card(
    full_screen = TRUE,
    card_header(
      class = "bg-dark",
      tags$a("Student Work Graded Dashboard", href = "https://teachinglabhq.shinyapps.io/student_work_graded/", style = "font-weight:bold;")
    ),
    card_image(
      file = "Images/Dashboards/StudentWorkGraded.png",
      href = "https://teachinglabhq.shinyapps.io/student_work_graded/"
    ),
    card_footer("View the % proficient and on grade level after assignments have been submitted and graded in the above dashboard.")
  )
)
```


<!-- <a href="https://youtu.be/mRBWfdjEv-4">End of Session Dashboard Tutorial</a>  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;<a href="https://youtu.be/dxE-PciN-ZY">Facilitator Facing Dashboard Tutorial</a> -->
<!-- <br> -->
<!-- <br> -->
<!-- &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; <a href="https://youtu.be/KZsLENMy8cg">End of Course Dashboard Tutorial</a> -->

<!-- ```{r active-dashboards, echo = F, layout = "l-page"} -->
<!-- library(bs4cards) -->

<!-- report_galleries <- tibble::tibble( -->
<!--   location = c( -->
<!--     "Facilitator facing dashboards", # 1 -->
<!--     "Coaching facing dashboards", # 2 -->
<!--     "Internal Participant Feedback Dashboard", # 3 -->
<!--     "Educator Survey Dashboard", # 4 -->
<!--     "Course Assessments Dashboard", # 5 -->
<!--     "IPG Dashboard", # 6 -->
<!--     "IPG Raw Data Dashboard", # 7 -->
<!--     "Student Survey Dashboard", # 8 -->
<!--     "EIC Student Survey Dashboard", # 9 -->
<!--     "Student Work Dashboard", # 10 -->
<!--     "Student Work Graded Dashboard" # 11 -->
<!--   ), -->
<!--   long_name = location, -->
<!--   text = c( -->
<!--     "A custom dashboard for use by teaching lab facilitators to view personal data (non FTE's)", -->
<!--     "A custom dashboard for use by teaching lab coaches to view personal data (non FTE's)", -->
<!--     "A Qualtrics dashboard to view all Participant Feedback, with tabs for viewing end of session, course, and coaching data separately", -->
<!--     "A Qualtrics dashboard to view all Educator Survey data, with tabs for different sections", -->
<!--     "A custom dashboard for diving deeper on responses to course assessments, including % all questions correct, % correct by question, and % selected for each answer", -->
<!--     "A Qualtrics dashboard for viewing all IPG data by % responses, split by rubric", -->
<!--     "A custom dashboard for looking at individual IPG responses, drill down by site -> coach -> teacher to see all available data", -->
<!--     "A Qualtrics dashboard for all Student Survey data, with tabs for each question grouping", -->
<!--     "A Qualtrics dashboard for all EIC Student Survey data, with tabs for each question grouping", -->
<!--     "A custom dashboard for grading student work", -->
<!--     "A custom dashboard for seeing the results of student work grading" -->
<!--   ), -->
<!--   image_url = c( -->
<!--     here::here("Images/Dashboards/FacilitatorFacingDashboard.png"), -->
<!--     here::here("Images/Dashboards/CoachingFacingDashboard.png"), -->
<!--     here::here("Images/Dashboards/QualtricsLogo.png"), -->
<!--     here::here("Images/Dashboards/QualtricsLogo.png"), -->
<!--     here::here("Images/Dashboards/CourseAssessment.png"), -->
<!--     here::here("Images/Dashboards/QualtricsLogo.png"), -->
<!--     here::here("Images/Dashboards/IPGRawDashboard.png"), -->
<!--     here::here("Images/Dashboards/QualtricsLogo.png"), -->
<!--     here::here("Images/Dashboards/QualtricsLogo.png"), -->
<!--     here::here("Images/Dashboards/StudentWorkGrader.png"), -->
<!--     here::here("Images/Dashboards/StudentWorkGraded.png") -->
<!--   ), -->
<!--   link = c( -->
<!--     "https://teachinglabhq.shinyapps.io/FacilitatorAuth/", # Facilitator board 1 -->
<!--     "https://teachinglabhq.shinyapps.io/CoachingAuth/", # Coaching board 2 -->
<!--     "https://teachinglab.co1.qualtrics.com/reporting-dashboard/web/6317cbd1f9feca001046524d", # End of Session 3 -->
<!--     "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/63053d35379f890010cc456e?pageId=Page_fcc6840b-679e-4652-b50c-6a95853b5887", # Educator Survey 4 -->
<!--     "https://teachinglabhq.shinyapps.io/course_assessments/", # Course Assessments 5 -->
<!--     "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/6349bfbbb614690016a0b7b1", # Classroom Observations 6 -->
<!--     "https://teachinglabhq.shinyapps.io/IPGRawDataDashboard/", -->
<!--     "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/6345c33160c27c00166cb726?pageId=Page_ee9d1195-c476-4414-b1ab-ee2da2fdb4ce", # Student Survey 8 -->
<!--     "https://teachinglab.co1.qualtrics.com/reporting-dashboard/#/dashboard/636172f94060140010530cc8?pageId=Page_35ff03a3-5111-48b5-abcd-ecfca4249e62", # EIC Student Survey 9 -->
<!--     "https://teachinglabhq.shinyapps.io/student_work_samples/", -->
<!--     "https://teachinglabhq.shinyapps.io/student_work_graded/" # 10 -->
<!--   ), -->
<!--   tags = c("custom", "custom", "qualtrics", "qualtrics", "custom", "qualtrics", "custom", "qualtrics", "qualtrics", "custom", "custom") -->
<!-- ) |> -->
<!--   dplyr::mutate( -->
<!--     label_color = ifelse(tags == "custom", "#04abeb", "#016891") -->
<!--   ) -->

<!-- report_galleries |> -->
<!--   cards( -->
<!--     title = "", -->
<!--     footer = long_name, -->
<!--     link = link, -->
<!--     text = text, -->
<!--     image = image_url, -->
<!--     layout = "label-left", -->
<!--     breakpoint = 5, -->
<!--     width = 4, -->
<!--     tags = paste("all;", tags), -->
<!--     label_colour = label_color, -->
<!--     spacing = 3 -->
<!--   ) -->
<!-- ``` -->

<!-- # Tutorials  -->

<!-- <br> -->

<!-- ```{r tutorials, echo = F} -->
<!-- galleries2 <- tibble::tibble( -->
<!--   long_name = c( -->
<!--     "Facilitator facing dashboards tutorial", -->
<!--     "NPS Dashboard Tutorial", -->
<!--     "IPG Dashboard Tutorial", -->
<!--     "Course Assessments Dashboard Tutorial" -->
<!--   ), -->
<!--   blurb = c( -->
<!--     "A tutorial for facilitators to see how to use the custom facilitator dashboard", -->
<!--     "A brief tutorial on the nps dashboard, overviewing what the data is and says.", -->
<!--     "An in depth tutorial on how to look at raw IPG data and download reports with fully developed visuals contextualizing the data.", -->
<!--     "Another in depth tutorial on how to see every level of course assessments data, from specific answers, to overall % correct." -->
<!--   ), -->
<!--   image_url = c("https://yt3.googleusercontent.com/584JjRp5QMuKbyduM_2k5RlXFqHJtQ0qLIPZpwbUjMJmgzZngHcam5JMuZQxyzGMV5ljwJRl0Q=s900-c-k-c0x00ffffff-no-rj"), -->
<!--   link = c("https://youtu.be/dxE-PciN-ZY", "https://youtu.be/t_QM7QxFUq8", "https://youtu.be/UtIpIyDLok4", "https://youtu.be/o0CEkx0r5yY"), -->
<!--   tags = c("all;custom;") -->
<!-- ) -->

<!-- galleries2 |> -->
<!--   cards( -->
<!--     title = long_name, -->
<!--     text = blurb, -->
<!--     link = link, -->
<!--     image = image_url, -->
<!--     layout = "label-below", -->
<!--     width = 2, -->
<!--     spacing = 3 -->
<!--   ) -->
<!-- ``` -->


<!-- # Visualizations -->

<!-- <br> -->

<!-- ```{r visualizations, echo = F} -->
<!-- time_diff <- Sys.Date() - as.Date("2019-01-01") -->
<!-- year_diff <- round(as.numeric(time_diff) / 365) -->
<!-- galleries3 <- tibble::tibble( -->
<!--   long_name = c( -->
<!--     "Visualizing and textualizing TL data.", -->
<!--     "How much does each US state spend per kid per capita over time?" -->
<!--   ), -->
<!--   blurb = c( -->
<!--     paste0("A visualization of ", year_diff, " years of reviews of Teaching Lab courses by type of content."), -->
<!--     "" -->
<!--   ), -->
<!--   image_url = c( -->
<!--     here::here("Images/Visualizations/Reviews.png"), -->
<!--     here::here("Images/Visualizations/SpendingperKid.png") -->
<!--   ), -->
<!--   link = c( -->
<!--     "https://teachinglab.github.io/TLReviews.html", -->
<!--     "https://teachinglab.github.io/USStateSpendingperKid.html" -->
<!--   ) -->
<!-- ) -->

<!-- galleries3 |> -->
<!--   cards( -->
<!--     title = long_name, -->
<!--     text = blurb, -->
<!--     link = link, -->
<!--     image = image_url, -->
<!--     layout = "label-below", -->
<!--     width = 2, -->
<!--     spacing = 3 -->
<!--   ) -->
<!-- ``` -->

<!-- # Inactive Dashboards (SY21-22) -->

<!-- <br> -->

<!-- All dashboards require an @teachinglab.org email login to verify that access to the correct content is granted. -->

<!-- <br> -->

<!-- ```{r inactive-dashboards-21-22, echo = F, layout = "l-page"} -->
<!-- # bs4cards::use_strapless(here::here("css")) -->
<!-- galleries <- tibble::tibble( -->
<!--   location = c("Facilitator End of Session Survey Dashboard", -->
<!--                 "End of Session Surveys 2021-2022", -->
<!--                 "End of Course Surveys 2021-2022",  -->
<!--                 "Survey Responses per Partner", -->
<!--                 "Coaching Participant Feedback 2022"), -->
<!--   long_name = location, -->
<!--   image_url = c(here::here("Images/Dashboards/FacilitatorPersonalDashboard.png"), -->
<!--                 here::here("Images/Dashboards/SessionDashboard.png"), -->
<!--                 here::here("Images/Dashboards/CourseDashboard.png"), -->
<!--                 here::here("Images/Dashboards/DiagnosticResponses.png"), -->
<!--                 here::here("Images/Dashboards/DiagnosticResponses.png")), -->
<!--   link = c("https://teachinglabhq.shinyapps.io/PersonalFacilitator/", -->
<!--            "https://teachinglabhq.shinyapps.io/SessionSurvey/", -->
<!--            "https://teachinglabhq.shinyapps.io/CourseSurvey/", -->
<!--            "https://teachinglabhq.shinyapps.io/DiagnosticComplete/", -->
<!--            "https://teachinglabhq.shinyapps.io/CoachingParticipantFeedback/") -->
<!-- ) -->

<!-- galleries |> -->
<!--   cards( -->
<!--     title = "Inactive Dashboards SY21-22", -->
<!--     link = link, -->
<!--     footer = long_name, -->
<!--     image = image_url, -->
<!--     layout = "label-below",  -->
<!--     width = 2,  -->
<!--     spacing = 3 -->
<!--   ) -->
<!-- ``` -->

<!-- <br> -->


<!-- # Inactive Dashboards (Pre SY20-21) -->

<!-- <br> -->

<!-- ```{r inactive-dashboards-20-21, echo = F} -->
<!-- galleries2 <- tibble::tibble( -->
<!--   location = c("End of Session Surveys before SY21-22"), -->
<!--   long_name = location, -->
<!--   image_url = c(here::here("Images/Dashboards/CourseDashboard.png")), -->
<!--   link = c("https://teachinglabhq.shinyapps.io/ParticipantFeedback/") -->
<!-- ) -->

<!-- galleries2 |> -->
<!--   cards( -->
<!--     title = "Inactive Dashboards SY20-21", -->
<!--     link = link, -->
<!--     footer = long_name, -->
<!--     image = image_url, -->
<!--     layout = "label-below",  -->
<!--     width = 2,  -->
<!--     spacing = 3 -->
<!--   ) -->
<!-- ``` -->

<!-- <br> -->
